Sparse spectral and $p$-finite element methods for partial differential equations on disk slices and trapeziums

### 2020-01-29 papers/disk-slices-and-trapeziums/revised/halfdisk.tex
add acknowledgment

\title{Sparse spectral and $p$-finite element methods for partial differential equations on disk slices and trapeziums}
\author{Sheehan Olver, Ben Snowball}
%\date{}							% Activate to display a given date or no date

@@

\noindent{\bf Acknowledgements}:  We would like to thank the anonymous referees for their helpful comments.  The second author was supported in part by a Leverhulme Trust Research Grant.

>>>>

\title{Sparse spectral and $p$-finite element methods for partial differential equations on disk slices and trapeziums}
\author{Sheehan Olver, Ben Snowball\thanks{Department of Mathematics, Imperial College, London, England}}
%\date{}							% Activate to display a given date or no date

@@

\noindent{\bf Acknowledgements}:  We would like to thank the anonymous referees for their helpful comments.  The second author was supported in part by the Leverhulme Trust Research Project Grant RPG-2019-144 ``Constructive approximation theory on and inside algebraic curves and surfaces.
